Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-09 automatica/paper.tex
tmp results update
(not final)

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                  \\
   &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
1  & Acrobot     & 4 & 16,8 & 61959.4\,s &  & ~\xmark \\
%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &14.6\,s \\
3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 9.2\,s \\
4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s \\
5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 67.6\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
6  & Cruise      & 1 & 16,8 & 9.6\,s & 16,10 & 6.5\,s \\
7 & CruiseHSCC & 1 & 16,8 & 9.6\,s & 16,10 & 6.6\,s  \\
8 & Cstr & 3 & & ~\xmark & & 19.842\,s \\
9 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark \\
10 & DCmotor   & 2 & 16,8  & 11.3\,s & 16,10 & 7.8\,s  \\
11 & Flexbeam   & 6 & & ~\xmark & & ~\xmark \\
12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
13 & Helicopter   & 3 & 16,8 & 13.8\,s & 32,23 & 148\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
14 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 16,10 & 28.2\,s\\
15 & Magpointer   & 2 & 16,8 & 10.1\,s & 16,10 & 20.4\,s \\
16 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 34.8\,s \\
17 & Pendulum   & 2 & 16,8 & 8.5\,s & 32,23 & 24\,s\\
%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
18 & streamdrum   & 3 & 16,8  & 332.5\,s & 16,10 & 590.5\,s \\
19 & Suspension  & 4 & 16,8  & 17.2\,s & 16,10 &1373\,s \\
20 & Tapedriver   & 3 & 16,8  & 8.2\,s & & ~\xmark \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}

>>>>

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                  \\
   &     & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$}& \multicolumn{1}{|c|}{Time}  \\\hline
1  & Acrobot     & 4 & 16,8 & 61529.8\,s &  & ~\xmark \\
%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
2  & Bioreact    & 3 & 16,8 & 11.5\,s & 16,10 &21.8\,s \\
3  & Chen\_ex1   & 3 & 16,8 & 10.3\,s  & 16,10 & 12.1\,s \\
4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
5  & Chen\_ex3   & 7 & 16,8  & 11.4\,s & 16,10 & 59.1\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
6  & Cruise      & 1 & 16,8 & 9.7\,s & 16,10 & 9.7\,s \\
7 & CruiseHSCC & 1 & 16,8 & 9.7\,s & 16,10 & 9.7\,s  \\
8 & Cstr & 3 & & ~\xmark & & 19.842\,s \\
9 & Cstrtmp  & 3 & 16,8 & 12.5\,s &16,10 & 14.4\,s \\
10 & DCmotor   & 2 & 16,8  & 10.0\,s & 16,10 & 11.4\,s  \\
11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
12 & Helicopter   & 3 &  & ~\xmark & 16,10 & 28.7\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
13 & Invpendulum\_pendang & 2 &  & ~\xmark & 16,10 & 13.8\,s\\
14 & Magpointer   & 2 &  & ~\xmark & 16,10 & 80.7\,s \\
15 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 16,10 & 42.3\,s \\
16 & Pendulum   & 2 & 16,8 & 13.6\,s & 16,10 & 16.1\,s\\
17 & Regulator   & 5 & & ~\xmark & 16,10 & 996.4\,s\\
18 & Springmassdamper & 2 & & ~\xmark &16,10 & 16.0s \\
19 & Streamdrum   & 3 & 16,8  & 700.9s & 16,10 & 24.4\,s \\
20 & Suspension  & 4 & 16,8  & 11.4\,s & 16,10 &15.4\,s \\
21 & Tapedriver   & 3 & 16,8  & 11.1\,s &16,10 & 13.2\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
